---
title: "Google User Study"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---

<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>

#folder structure

+-- 2020-google-user-study.Rproj
+-- plots <-  folder for final and polished charts and maps
+-- proc_data <- folder for all data that has been processed or saved from the raw files 
+-- raw_data <- folder for raw data files
+-- README.md
\-- rmd
    +-- analysis.Rmd <- file for modeling data and polishing charts
    \-- final.Rmd <- final file with polished graphs and results description


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
```

```{r additional_packages}
if (!requireNamespace("waffle")) install.packages("waffle")
```



```{r prep}
## packages
library(tidyverse)
library(tidytext)
library(colorspace)
library(sf)
library(maps)
library(albersusa) # remotes::install_github("hrbrmstr/albersusa")
library(rgeocodio) # remotes::install_github("hrbrmstr/rgeocodio")
library(geojsonio)
library(rgeos)
library(ggwordcloud)
library(patchwork)
library(pdftools)
library(showtext)

## save plots?
save <- TRUE
#save <- FALSE

## quality of png's
dpi <- 750

## font
font_add_google("Montserrat", "Montserrat")
font_add_google("Overpass", "Overpass")
font_add_google("Overpass Mono", "Overpass Mono")

## theme updates
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))

theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 22,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40", 
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "Montserrat") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main color backlinko
bl_col <- "#00d188"

## colors + labels for interval stripes
int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")

## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
cols_degree <- c("#e64500", "#FFCC00", darken(bl_col, .1))

## gradient colors for position
colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
pos_cols <- colfunc(10)
```


```{r saving plots, eval = FALSE}
#saving plots function example

if (save == T){
  ggsave(here::here("plots", "1_1_jobs_word.pdf"), width = 12, height = 11, device = cairo_pdf)

```


# 0. Data

## Read our fetched data from google sheets

```{r}
sheets <- readRDS(here::here("proc_data/fetched_data.RDS"))
```

## tidy the data into one clean table

Check consistency of column names

```{r}
name_summary <- 
  sheets %>% 
  map_dfr(~ tibble(nm = colnames(.)), .id = "sheet_name") %>%
  spread(nm, nm) %>%
  mutate_at(-1, ~ !is.na(.))

inconsistent_cols <- Filter(Negate(all), name_summary[-1])

# show columns that are not on every question
inconsistent_cols
```

We need to fix typos and harmonise some names, we also remove the col "..19" as it's just an unnamed empty column.

```{r}
for (nm in names(sheets)) {
  sheets[[nm]][["...19"]] <- NULL
  names(sheets[[nm]]) <- sub("organis ", "organic ", names(sheets[[nm]]))
  names(sheets[[nm]]) <- sub("different ULRs/pages", "pages", names(sheets[[nm]]))
}

# now we try again
name_summary <- 
  sheets %>% 
  map_dfr(~ tibble(nm = colnames(.)), .id = "sheet_name") %>%
  spread(nm, nm) %>%
  mutate_at(-1, ~ !is.na(.))

inconsistent_cols <- Filter(Negate(all), name_summary[-1])
if (ncol(inconsistent_cols)) stop("we still have inconsistent column names")
```

Now that we have consistent column names, we must ensure we have consistent type.

```{r}
type_summary <- 
  sheets %>% 
  map_dfr(summarize_all, typeof, .id = "sheet_name")

inconsistent_cols <- Filter(function(x) n_distinct(x) != 1, type_summary[-1])

if (ncol(inconsistent_cols)) stop("we have inconsistent columns types")
```

We can now concatenate the data of all questions in a single table

```{r}
full_data <- bind_rows(sheets, .id = "question")
# remove row containing only NAs appart from é first columns
full_data <- full_data[rowSums(is.na(full_data)) != ncol(full_data) - 2,]
# convert Y/N/y/n to TRUE/FALSE
full_data <- modify_if(full_data, ~all(tolower(unique(.)) %in% c("y","n")), ~ tolower(.) == "y")
```

We observe that item "If clicked on Google Maps/local listing, did they click on 
one of the first three listings?" was assigned "N" when it is not relevant 
(no click on google map listing) so we fix by setting those to `NA`.

```{r}
full_data[["If clicked on Google Maps/local listing, did they click on one of the first three listings?"]] <- 
  ifelse(full_data[["Clicks on Google Maps/local listings"]],
         full_data[["If clicked on Google Maps/local listing, did they click on one of the first three listings?"]],
         NA)

saveRDS(full_data, here::here("proc_data/clean_data.RDS"))
```

# 1. Raw analysis

We go through all items and drive out key insights.

```{r}
plots <- list()
```


<!-- ## logical variables -->

<!-- percentage of use by question and total -->

<!-- ```{r} -->
<!-- lgl_by_q <- full_data %>% -->
<!--   group_by(question) %>% -->
<!--   summarize_if(is.logical, ~  100*mean(., na.rm = TRUE)) -->

<!-- lgl_by_q -->

<!-- lgl_by_q %>% -->
<!--   summarize_if(is.numeric, ~  mean(., na.rm = TRUE)) -->
<!-- #  -->
<!-- full_data %>% -->
<!--   summarize_if(is.logical, ~  100*mean(., na.rm = TRUE)) -->
<!-- ``` -->

<!-- We showed two aggregated summaries here, one is averaged over the questions,  -->
<!-- and one is averaged over individual observations. They amount to the same in -->
<!-- the 2 former cases, not so much in the last one. I'm not convinced that the  -->
<!-- question "If clicked on Google Maps/local listing, did they click on one of the first three listings?" -->
<!-- should be used as it seems to suffer from low sample size. -->

## When typing the search query, did they select one of the suggested searches? (Y/N)

```{r}
item <- "When typing the search query, did they select one of the suggested searches? (Y/N)"
if (names(full_data)[[3]] != item)
  stop("wrong order of columns")

plots[[item]] <- full_data %>%
  group_by(question) %>%
  summarize_at(item, ~100*mean(.)) %>%
  arrange_at(item) %>%
  mutate(fill = "a") %>%
  bind_rows(summarise_at(., 2, mean) %>% mutate(question = "Overall", fill = "b")) %>%
  mutate(question = factor(question, question)) %>%
  ggplot() +
  geom_col(aes(
    question, 
    !!sym(item),
    fill = fill)) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 30, hjust = 1)) +
  ggtitle(item) +
  labs(x = "", y = "% of users who selected a suggestion")

plots[[item]]
```

## Seconds to first click (use check time stamping on video)

```{r}
item <- "Seconds to first click (use check time stamping on video)"
if (names(full_data)[[4]] != item)
  stop("wrong order of columns")

full_data %>%
  group_by_at(4) %>%
  summarize(n = n()) %>%
  ggplot(aes(!!sym(item), n)) +
  geom_point() +
  geom_line() +
  ggtitle("raw chart")
```

```{r}
plot_data <- full_data %>%
  group_by_at(4) %>%
  summarize(pct = n()/nrow(.)) %>%
  mutate_at("pct", cumsum) 

# quantile data with labels
q_data = tibble(
    q = quantile(full_data[[item]], c(.25,.5,.75)), 
    x = approx(plot_data$pct, plot_data[[item]], xout = c(.25,.5,.75))$y,
    y = c(.25,.50,.75),
    lab = sprintf("%s%% click before %s sec", y*100, q))

plots[[item]] <- plot_data %>%
  ggplot(aes(!!sym(item), pct))  + 
  geom_line() +
  coord_cartesian(xlim = c(0,50)) + 
  ggtitle("Time to first click") +
  labs(x = "time (seconds)", y = "% of users who click before time") +
  geom_point(aes(x,y), data =q_data, size = 4) +
  geom_text(aes(x,y, label = lab), data = q_data, hjust = 0, nudge_x = 3) +
  scale_y_continuous(labels = function(x) scales::percent(x,1))

plots[[item]]
```

## Did they scroll to the end of the Google Search Page (Y/N)?

```{r}
item <- "Did they scroll to the end of the Google Search Page (Y/N)?"
if (names(full_data)[[5]] != item)
  stop("wrong order of columns")

plots[[item]] <- full_data %>%
  group_by(question) %>%
  summarize_at(item, ~100*mean(.)) %>%
  arrange_at(item) %>%
  mutate(fill = "a") %>%
  bind_rows(summarise_at(., 2, mean) %>% mutate(question = "Overall", fill = "b")) %>%
  mutate(question = factor(question, question)) %>%
  ggplot() +
  geom_col(aes(
    question, 
    !!sym(item),
    fill = fill)) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 30, hjust = 1)) +
  ggtitle(item) +
  labs(x = "", y = "% of users who scrolled to the bottom")
plots[[item]]
```

## Times changed/modified search query


```{r}
item <- "Times changed/modified search query"
if (names(full_data)[[6]] != item)
  stop("wrong order of columns")

table(full_data[[6]])

plots[[item]] <- full_data %>%
  transmute_at(item, ~ifelse(.>1, "2+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of changes", y = "% of users")

plots[[item]]
```

## Times searcher clicks a result, then bounces back to the search results page and chooses a different result

```{r}
item <- "Times searcher clicks a result, then bounces back to the search results page and chooses a different result"
table(full_data[[7]])
```

```{r}
plots[[item]] <- full_data %>%
  transmute_at(item, ~ifelse(.>1, "2+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks followed by bounces", y = "% of users")

plots[[item]]
```

## Number of pages visited

```{r}
item <- "Number of pages visited"
table(full_data[[item]])
```

```{r}
plots[[item]] <- full_data %>%
  transmute_at(item, ~ifelse(.>=4, "4+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of pages", y = "% of users")

plots[[item]]
```

## Clicks on organic search results

```{r}
item <- "Clicks on organic search results"
table(full_data[[item]])
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=3, "3+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]]
```


## Clicks on Google AdWords/paid listings

```{r}
item <- "Clicks on Google AdWords/paid listings"
table(full_data[[item]])
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=2, "2+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]] 
```




## Clicks on video results

```{r}
item <- "Clicks on video results"
table(full_data[[item]])
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=2, "2+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]] 
```

## Clicks on Google Maps/local listings

```{r}
item <- "Clicks on Google Maps/local listings"
table(full_data[[item]])
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=2, "2+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]]
```


## If clicked on Google Maps/local listing, did they click on one of the first three listings?

```{r}
item <- "If clicked on Google Maps/local listing, did they click on one of the first three listings?"
table(full_data[[item]], full_data[["question"]], useNA = "always")
```

```{r}
full_data %>%
  group_by(question) %>%
  summarize(clickers = sum(`Clicks on Google Maps/local listings` != 0), first3 = 100*mean(!!sym(item), na.rm = TRUE))

full_data %>%
  summarize(clickers = sum(`Clicks on Google Maps/local listings` != 0), first3 = 100*mean(!!sym(item), na.rm = TRUE))
```

We don't have reliable numbers here for any conclusion

## Clicks on Image blocks

```{r}
item <- "Clicks on Image blocks"
table(full_data[[item]], useNA = "always")
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=1, "1+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]]
```

Here let's make sure that the instruction and measurement were ok because number
is really low

## Clicks on Google Shopping results

```{r}
item <- "Clicks on Google Shopping results"
table(full_data[[item]], useNA = "always")
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=1, "1+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]]
```


## Clicks "people also ask" box

```{r}
item <- "Clicks \"people also ask\" box"
table(full_data[[item]], useNA = "always")
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=1, "1+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]]
```


## Clicks to 2nd+ Google page

```{r}
item <- "Clicks to 2nd+ Google page"
table(full_data[[item]], useNA = "always")
```

```{r}
plots[[item]] <-
  full_data %>%
  transmute_at(item, ~ifelse(.>=1, "1+", .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col() +
  ggtitle(item) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "number of clicks", y = "% of users")

plots[[item]] 
```


## Seconds to complete search task

```{r}
item <- "Seconds to complete search task"

full_data %>%
  group_by_at(item) %>%
  summarize(n = n()) %>%
  ggplot(aes(!!sym(item), n)) +
  geom_point() +
  geom_line() +
  ggtitle("raw chart")
```

```{r}
# quantile data with labels

plot_data <- full_data %>%
  group_by_at(item) %>%
  summarize(pct = n()/nrow(.)) %>%
  mutate_at("pct", cumsum) 

q_data = tibble(
    q = quantile(full_data[[item]], c(.25,.5,.75)), 
    x = approx(plot_data$pct, plot_data[[item]], xout = c(.25,.5,.75))$y,
    y = c(.25,.50,.75),
    lab = sprintf("%s%% complete before %s sec", y*100, q))


plots[[item]] <-
  plot_data %>%
  ggplot(aes(!!sym(item), pct))  + 
  geom_line() +
  coord_cartesian(xlim = c(0,300)) + 
  ggtitle("Time to complete a search task") +
  labs(x = "time (seconds)", y = "% of users who complete the task before time") +
  geom_point(aes(x, y), data =q_data, size = 4) +
  geom_text(aes(x, y, label = lab), data = q_data, hjust = 0, nudge_x = 3) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) 

plots[[item]]
```


## Total Clicks

```{r}
item <- "Total Clicks"
table(full_data[[item]], useNA = "always")
```

```{r}
# quantile data with labels


plot_data <- full_data %>%
  group_by_at(item) %>%
  summarize(pct = n()/nrow(.)) %>%
  mutate_at("pct", cumsum) 

q_data = tibble(
    q = quantile(full_data[[item]], c(.25,.5,.75)), 
    x = approx(plot_data$pct, plot_data[[item]], xout = c(.25,.5,.75))$y,
    y = c(.25,.50,.75),
    lab = sprintf("%s%% click less than %s times", y*100, q))

plots[[item]] <-
  plot_data %>%
  ggplot(aes(!!sym(item), pct))  + 
  geom_line() +
  #geom_point() +
  coord_cartesian(xlim = c(0,50)) + 
  ggtitle("Total number of clicks") +
  labs(x = "number of clicks", y = "% of users who clicked less than the given numeber of clicks") +
  geom_point(aes(x, y), data = q_data, size = 4) +
  geom_text(aes(x, y, label = lab), data = q_data, hjust = 0, nudge_x = 3) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) 

plots[[item]]
```


# 2. Save Results

```{r}
saveRDS(plots, here::here("proc_data/plots.RDS"))
```

