---
title: "Google User Study"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: console
---

<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>

#folder structure

+-- 2020-google-user-study.Rproj
+-- plots <-  folder for final and polished charts and maps
+-- proc_data <- folder for all data that has been processed or saved from the raw files 
+-- raw_data <- folder for raw data files
+-- README.md
\-- rmd
    +-- analysis.Rmd <- file for modeling data and polishing charts
    \-- final.Rmd <- final file with polished graphs and results description


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```

```{r prep}
## packages
#library(Hmisc)
library(tidyverse)
library(colorspace)
library(pdftools)
library(showtext)

## save plots?
save <- TRUE
#save <- FALSE

## quality of png's
dpi <- 750

## font
#extrafont::loadfonts(device = "win", quiet = TRUE)
#font_add_google("Montserrat", "Montserrat")
# font_add_google("Overpass", "Overpass")
# font_add_google("Overpass Mono", "Overpass Mono")

## theme updates
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat"))


theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "Montserrat") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")

## colors + labels for interval stripes
int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")

## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
cols_degree <- c("#e64500", "#FFCC00", darken(bl_col, .1))

## gradient colors for position
colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
pos_cols <- colfunc(10)
```

# 0. Data

## load

```{r}
full_data <- readRDS(here::here("proc_data/clean_data.RDS"))
participants <- readRDS(here::here("proc_data/participants.RDS"))
```


## define descriptions for the different questions

```{r}
# Commercial_1_pyhsical: find a car phone holder (assumption: Google shopping results)
# Commercial_2_service: find a credit card (assumptions: affiliate articles)
# Local: find a car accident lawyer (assumptions: ads)
# Informational_1: find how to cut your own hair (assumptions: videos)
# Informational_2: find how to treat back pain (assumptions: in-depth articles)
# Transactional: find supplements that may help with lower back pain
# Commercial_3_service: buy groceries online in your local area
question_descs <- c(
  Q1_Commercial_1_pyhsical = "find a car phone holder",
  Q2_Commercial_2_service = "find a credit card",
  Q3_Local = "find a car accident lawyer",
  Q4_Informational_1_video = "find how to cut your own hair",
  Q5_Informational_2_indeepth = "find how to treat back pain",
  Q6_transactional = "find supplements to treat back pain",
  Q7_Commercial_3_service = "buy groceries online"
)
```


# 1. Raw analysis

We go through all items and drive out key insights. First w define the plotting
functions that we'll use

```{r}
plots <- list()

save_plot <- function(plot, item, width, height) {
  if (save)
    #ggsave(here::here("plots", paste0(make.names(item), ".pdf")), plots[[item]], width = 12, height = 11, device = cairo_pdf)
    #ggsave(here::here("plots", paste0(make.names(item), ".png")), plot, width = 12, height = 11)
    ggsave(here::here("plots", paste0(make.names(item), ".pdf")), plot, width = width, height = height, device = cairo_pdf)
}

lollipop_chart <- function(full_data, item, title, xlab, nudge_x = 0, percent = TRUE, fun = ~mean(., na.rm = TRUE), digits = 1) {
  summary_by_q <-
    full_data %>%
    mutate(question = question_descs[question]) %>%
    group_by(question) %>%
    summarize_at(item, fun) %>%
    mutate(group = "a")
  
  summary_overall <-
    full_data %>%
    summarize_at(item, fun) %>%
    mutate(question = "Overall", group = "b")
  
  summary_all <- 
    bind_rows(summary_by_q, summary_overall) %>%
    arrange_at(item) %>%
    mutate(question = Hmisc::capitalize(question)) %>% 
    mutate(question = factor(question, question)) # sort factors
  
  ggplot(summary_all) +
    geom_segment(aes(y= question, yend = question, x = 0, xend = !!sym(item),
                     color = group), size = 2) + 
    geom_point(aes(x = !!sym(item), y = question, color = group), size = 7) +
    geom_text(data = summary_overall,
              aes(!!sym(item), question, label = if(percent) scales::percent(!!sym(item), digits) else round(!!sym(item), digits)), color = bl_dark, 
              hjust = 0, nudge_x = nudge_x, family = "Montserrat", fontface = "bold") +
    labs(x = xlab, y = "") +
    scale_color_manual(values = c(bl_col, bl_dark)) +
    {if (percent) scale_x_continuous(labels = function(x) scales::percent(x, digits))} +
    ggtitle(title) +
    theme(legend.position = "none")
}
  
# item <- "Seconds to first click (use check time stamping on video)"

quantile_chart <- function(full_data, item, title, xlab, ylab, qlab, meanlab, xmax, 
                           nudge_x, digits = 1){
  plot_data <- full_data %>%
    group_by_at(item) %>%
    summarize(pct = n()/nrow(.)) %>%
    mutate_at("pct", cumsum) 
  
  x_mean <- mean(full_data[[item]])
  
  mean_data <- tibble(
    x = mean(full_data[[item]]),
    y = approx(plot_data[[item]], plot_data$pct, xout = x_mean)$y,
    lab = sprintf(meanlab, round(x_mean, 1))
  )
  
  q_data = tibble(
    q = quantile(full_data[[item]], c(.25,.5,.75)), 
    x = approx(plot_data$pct, plot_data[[item]], xout = c(.25,.5,.75))$y,
    y = c(.25,.50,.75),
    lab = sprintf(qlab, y*100, q))
  
  plot_data %>%
    ggplot(aes(!!sym(item), pct))  + 
    geom_line(color = "grey30") +
    coord_cartesian(xlim = c(0,xmax)) + 
    ggtitle(title) +
    labs(x = xlab, y = ylab) +
    geom_point(aes(x,y), data = q_data, size = 4, color = "grey30") +
    geom_point(aes(x,y), data = mean_data, color = bl_col, size = 4) +
    geom_text(aes(x,y, label = lab), data = q_data, hjust = 0, nudge_x = nudge_x, family = "Montserrat", color = "grey30", fontface = "bold") +
    geom_text(aes(x,y, label = lab), data = mean_data, hjust = 0, nudge_x = nudge_x, family = "Montserrat", color = bl_col, fontface = "bold") +
    scale_y_continuous(labels = function(x) scales::percent(x, digits))
}

quantile_chart2 <- function(full_data, item, title, xlab, ylab, qlab, meanlab, xmax, 
                           nudge_x, digits = 1){
  plot_data <- 
    full_data %>%
    # trim unnecessary cols
    select(question, !!sym(item)) %>%
    # use readable name
    mutate(question = question_descs[question]) %>%
    # create columns with aggregated values (but not aggregating the rest => mutate not summarize)
    group_by(question) %>% 
    mutate(x_avg = mean(!!sym(item)),
           x_q1 = quantile(!!sym(item), 0.25),
           x_q2 = quantile(!!sym(item), 0.5),
           x_q3 = quantile(!!sym(item), 0.75),
           n_by_question = n()) %>%
    # aggregate to count percentage for each time and each question
    group_by(!!sym(item), question, x_avg, x_q1, x_q2, x_q3, n_by_question) %>%
    summarize(pct = n()/n_by_question[1]) %>%
    # retur to question level to cumulate the pct and project quantiles and mean on curve
    group_by(question) %>% 
    mutate_at("pct", cumsum) %>%
    mutate(y_avg = approx(!!sym(item), pct, xout = x_avg)$y,
           y_q1 = approx(!!sym(item), pct, xout = x_q1)$y,
           y_q2 = approx(!!sym(item), pct, xout = x_q2)$y,
           y_q3 = approx(!!sym(item), pct, xout = x_q3)$y,
           lab_avg = sprintf(meanlab, round(x_avg, 1)),
           lab_q1 = sprintf(qlab, 25, x_q1),
           lab_q2 = sprintf(qlab, 50, x_q2),
           lab_q3 = sprintf(qlab, 75, x_q3)) %>%
    ungroup()
    
  
  plot_data %>%
    ggplot(aes(!!sym(item), pct))  + 
    geom_line() +
    coord_cartesian(xlim = c(0,xmax)) + 
    ggtitle(title) +
    labs(x = xlab, y = ylab) +
    geom_point(aes(x_q1,y_q1), size = 4, color = "grey30") +
    geom_point(aes(x_q2,y_q2), size = 4, color = "grey30") +
    geom_point(aes(x_q3,y_q3), size = 4, color = "grey30") +
    geom_point(aes(x_avg, y_avg), color = bl_col, size = 4, color = "grey30") +
    geom_text(aes(x_q1, y_q1, label = lab_q1), hjust = 0, nudge_x = nudge_x, family = "Montserrat", color = "grey30") +
    geom_text(aes(x_q2, y_q2, label = lab_q2), hjust = 0, nudge_x = nudge_x, family = "Montserrat", color = "grey30") +
    geom_text(aes(x_q3, y_q3, label = lab_q3), hjust = 0, nudge_x = nudge_x, family = "Montserrat", color = "grey30") +
    geom_text(aes(x_avg, y_avg, label = lab_avg), hjust = 0, nudge_y = -0.05, family = "Montserrat", color = bl_col, fontface = "bold") +
    scale_y_continuous(labels = function(x) scales::percent(x, digits)) +
    facet_wrap("question", ncol = 2)
}

bar_chart <- function(full_data, item,title, xlab, ylab, threshold) {
  full_data %>%
  transmute_at(item, ~ifelse(.>= threshold, paste0(threshold, "+"), .)) %>%
  group_by_at(item) %>%
  count() %>%
  ungroup() %>%
  mutate(n = n/sum(n)) %>%
  na.omit() %>%
  ggplot(aes(!!sym(item),n)) +
  geom_col(fill = bl_col,color = bl_dark) +
  geom_text(aes(label = scales::percent(n,1)), vjust = 0, nudge_y = .02, family = "Montserrat") +
  ggtitle(title) +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = xlab, y = ylab)
}
```

## 1.0 participant stats

```{r}
engine_data <-
  participants %>%
  rename_at(4, ~"fav_engine") %>%
  count(fav_engine) %>%
  na.omit() %>%
  mutate(ratio = n/sum(n))


# we see that 94% use google, let's show the rest separately
plots[["engines"]] <-
  participants %>%
  rename_at(4, ~"fav_engine") %>%
  mutate(fav_engine = ifelse(fav_engine == "Google", "Google", "Competitors")) %>%
  count(fav_engine) %>%
  na.omit() %>%
  mutate(ratio = n/sum(n)) %>%
  arrange(desc(ratio)) %>%
  mutate(fav_engine = factor(fav_engine, fav_engine)) %>%
  ggplot(aes(fav_engine, ratio)) +
  geom_col(fill = bl_col,color = bl_dark) +
  geom_text(aes(label = scales::percent(ratio,.1)), vjust = 0, nudge_y = .02, family = "Montserrat") +
  ggtitle("94% of Users Most Commonly Use Google") +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "", y = "% of users")

plots[["engines2"]] <-
  participants %>%
  rename_at(4, ~"fav_engine") %>%
  count(fav_engine) %>%
  na.omit() %>%
  mutate(ratio = n/sum(n)) %>%
  filter(fav_engine != "Google") %>%
  arrange(desc(ratio)) %>%
  mutate(fav_engine = factor(fav_engine, fav_engine)) %>%
  ggplot(aes(fav_engine, ratio)) +
  geom_col(fill = bl_col,color = bl_dark) +
  geom_text(aes(label = scales::percent(ratio,.1)), vjust = 0, nudge_y = .001, family = "Montserrat") +
  ggtitle("Most Commonly Used Browser among Google Competitors") +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "", y = "% of users")

save_plot(plots[["engines"]], "engines", 9, 6.5)
save_plot(plots[["engines2"]], "engines2", 9, 6.5)



plots[["how_do_you_use_gs"]] <-
  participants %>%
  rename_at(5, ~"how_do_you_use_gs") %>%
  count(how_do_you_use_gs) %>%
  na.omit() %>%
  mutate(ratio = n/sum(n)) %>%
  arrange(desc(ratio)) %>%
  mutate(how_do_you_use_gs = factor(how_do_you_use_gs, how_do_you_use_gs)) %>%
  ggplot(aes(how_do_you_use_gs, ratio)) +
  geom_col(fill = bl_col,color = bl_dark) +
  geom_text(aes(label = scales::percent(ratio,.1)), vjust = 0, nudge_y = .01, family = "Montserrat") +
  ggtitle("Frequency of Use of Google Search") +
  scale_y_continuous(labels = function(x) scales::percent(x,1)) +
  labs(x = "", y = "% of users")

save_plot(plots[["how_do_you_use_gs"]], "how_do_you_use_gs", 9.5, 7.5)
```

## 1.1 When typing the search query, did they select one of the suggested searches? (Y/N)

```{r}
item <- "When typing the search query, did they select one of the suggested searches? (Y/N)"

plots[[item]] <- lollipop_chart(
  full_data, item,
  "Commercial and Transaction Queries Lead to More\nGoogle Autocomplete Suggestions Being Used", "% of users who selected a suggestion",
  nudge_x = .01, fun = ~mean(. != 0, na.rm = TRUE))

save_plot(plots[[item]], item, 10, 6.5)
```

## 1.2 Seconds to first click

```{r}
item <- "Seconds to first click (use check time stamping on video)"

# full_data %>%
#   group_by_at(4) %>%
#   summarize(n = n()) %>%
#   ggplot(aes(!!sym(item), n)) +
#   geom_point() +
#   geom_line() +
#   ggtitle("raw chart")

plots[[item]] <- quantile_chart(
  full_data, item,
  "50% of Google Users Click Within 9 Seconds of Their Search",
  "Time (seconds)", "% of users who click before time",
  meanlab = "Average: %s sec", qlab = "%s%% click before %s sec",
  xmax = 50, nudge_x = 1.2)

save_plot(plots[[item]], item, 9, 7)


## might need soem additional work
item_facets <- paste0(item,"_facets")
plots[[item_facets]] <- quantile_chart2(
  full_data, item,
  "Time Before First Click by Question",
  "Time (seconds)", "% of users who click before time",
  meanlab = "Average: %s sec", qlab = "%s%% click before %s sec",
  xmax = 50, nudge_x = 3)

save_plot(plots[[item_facets]], item_facets, 14, 16)

item2 <- paste0(item,"_2")

plots[[item2]] <- lollipop_chart(
  full_data, item,
  "The Average Time to First Click Spans from 10 to 25 Seconds", "Time (seconds)",
  nudge_x = 1, percent = FALSE)

save_plot(plots[[item2]], item2, 10, 6.5)
```

## 1.3 Scrolling to the end of the search page

```{r}
item <- "Did they scroll to the end of the Google Search Page (Y/N)?"

plots[[item]] <- lollipop_chart(
  full_data, item,
  "9% of Users Scroll to the Bottom of the First Page\n(Although This Is Highly Dependent On the Search Query)", 
  "% of users who scrolled to the bottom", nudge_x = .007)
plots[[item]]

save_plot(plots[[item]], item, 10, 6.5)
```

## 1.4 Times changed/modified search query

```{r}
item <- "Times changed/modified search query"

table(full_data[[6]])

plots[[item]] <-  bar_chart(
  full_data, item,
  "85% of the Time, Users Stick to their First Choice of Query",
   "Number of changes", "% of users", 2)
save_plot(plots[[item]], item, 9, 6.5)

item2 <- paste0(item,"_2")
plots[[item2]] <- lollipop_chart(
  full_data, item,
  "Percentage of Users Who Modify their Query", "", 
  fun = ~mean(. != 0, na.rm = TRUE),
  nudge_x = .013)

save_plot(plots[[item2]], item2, 10, 6.5)
```

## 1.5 Times searcher clicks a result, then bounces back to the search results page and chooses a different result

```{r}
item <- "Times searcher clicks a result, then bounces back to the search results page and chooses a different result"
table(full_data[[7]])

plots[[item]] <- bar_chart(
  full_data, item,
  "83% of Google Searchers Don’t Bounce Back to the SERPs", "Number of clicks followed by bounces",  "% of users", 2)

save_plot(plots[[item]], item, 9, 6.5)

item2 <- paste0(item,"_2")
plots[[item2]] <- lollipop_chart(
  full_data, item,
  "Bounce Rate Varies Depending On Type of Query", "% of users who bounce at least once", 
  fun = ~mean(. != 0, na.rm = TRUE), nudge_x = .013)

save_plot(plots[[item2]], item2, 10, 6.5)
```

## 1.6 Number of pages visited

```{r}
item <- "Number of pages visited"
table(full_data[[item]])

plots[[item]] <- 
  bar_chart(
    full_data, item,
    "59% of Google Users Click on a Single\nResult During Their Search Session", "Number of pages visited", 
    "% of users", threshold = 4)

save_plot(plots[[item]], item, 9, 6.5)

item2 <- paste0(item,"_2")
plots[[item2]] <- lollipop_chart(
    full_data, item,
    "Average Number of Visited Pages", "", 
    nudge_x = .08,
    percent = FALSE)

save_plot(plots[[item2]], item2, 10, 6.5)
```

## 1.7 Clicks on organic search results

```{r}
item <- "Clicks on organic search results"
table(full_data[[item]])

plots[[item]] <- bar_chart(
  full_data, item,
  "65% of Google Searchers Click On the Organic Results",
  "Number of clicks", "% of users",
  threshold = 3)

save_plot(plots[[item]], item, 9, 6.5)

item2 <- paste0(item,"_2")
plots[[item2]] <- lollipop_chart(
  full_data, item,
  "Percentage of Users Who Click on Organic Search Results", "", 
  nudge_x = .03,
  percent = TRUE,
  fun = ~mean(. != 0, na.rm = TRUE))

save_plot(plots[[item2]], item2, 10, 6.5)
```


## 1.8 Clicks on Google AdWords/paid listings

```{r}
item <- "Clicks on Google AdWords/paid listings"
table(full_data[[item]])

plots[[item]] <- bar_chart(
  full_data, item,
  "19% of Users Click on a Google Ad",
  "Number of clicks", "% of users", 2)

save_plot(plots[[item]], item, 9, 6.5)

item2 <- paste0(item,"_2")
plots[[item2]] <- lollipop_chart(
  full_data, item,
  "Commercial and Transactional Queries Generate More\nGoogle Ad Clicks Than Informational Queries", "", 
  nudge_x = .012,
  percent = TRUE,
  fun = ~mean(. != 0, na.rm = TRUE))

save_plot(plots[[item2]], item2, 10, 6.5)
```


## 1.9 Clicks on video results

```{r}
item <- "Clicks on video results"
table(full_data[[item]])

plots[[item]] <- bar_chart(
  full_data, item,
  "Clicks on Video Results",  "Number of clicks", "% of users", 2)
save_plot(plots[[item]], item, 9, 6.5)

item2 <- paste0(item,"_2")
plots[[item2]] <- lollipop_chart(
  full_data, item,
  "Users are much more likely to click on video results\nif they look for how to cut one's hair",
  "% of users who click on video results", 
  nudge_x = .03,
  percent = TRUE,
  fun = ~mean(. != 0, na.rm = TRUE))

save_plot(plots[[item2]], item2, 10, 6.5)
```

## 1.10 Clicks on Google Maps/local listings

```{r}
item <- "Clicks on Google Maps/local listings"
table(full_data[[item]])

plots[[item]] <- bar_chart(
  full_data, item,
  "In 94% of Searches, the User Won't Click\non Maps or Local Listings", "Number of clicks", "% of users who click on Maps or local listings", 2)

save_plot(plots[[item]], item, 9, 7)

item2 <- paste0(item,"_2")
plots[[item2]] <- lollipop_chart(
  full_data, item,
  "Users are Much more Likely to Click on Google Maps or\nLocal Listings if They Look for a Car Accident Lawyer",
  "% of users who click on Google Maps or local listings", 
  nudge_x = .015,
  percent = TRUE,
  fun = ~mean(. != 0, na.rm = TRUE))

save_plot(plots[[item2]], item2, 10, 6.5)
```


## 1.11 If clicked on Google Maps/local listing, did they click on one of the first three listings?

No plot here, we'll share the conclusion in text

```{r}
item <- "If clicked on Google Maps/local listing, did they click on one of the first three listings?"
table(full_data[[item]], full_data[["question"]], useNA = "always")

full_data %>%
  group_by(question) %>%
  summarize(clickers = sum(`Clicks on Google Maps/local listings` != 0), first3 = 100*mean(!!sym(item), na.rm = TRUE))

full_data %>%
  summarize(clickers = sum(`Clicks on Google Maps/local listings` != 0), first3 = 100*mean(!!sym(item), na.rm = TRUE))
```

## 1.12 Clicks on Image blocks

We measure how often users click on image blocks and find that they click on them
less than half a percent of the time.

Note to Daniel : probably better not to include this at all

better check that the instruction and measurement were ok because number
is really low

```{r}
item <- "Clicks on Image blocks"
table(full_data[[item]], useNA = "always")
scales::percent(mean(full_data[[item]] != 0, na.rm = TRUE))
```

## 1.13 Clicks on Google Shopping results

```{r}
item <- "Clicks on Google Shopping results"
table(full_data[[item]], useNA = "always")

plots[[item]] <- lollipop_chart(
  full_data, item, 
  "Users are more Likely to Click on Google Shopping Results\nif They Look for Supplements to Treat Back Pain", "% of users who click on Google Shopping results",
  fun = ~ mean(.!=0, na.rm =TRUE), nudge_x = .007)

save_plot(plots[[item]], item, 10, 6.5)
```


## 1.14 Clicks "people also ask" box

```{r}
item <- "Clicks \"people also ask\" box"
table(full_data[[item]], useNA = "always")

plots[[item]] <- lollipop_chart(
  full_data, item, 
  "Users are more Likely to Click on \"People also Ask\" Box\nif They Look for Supplements to Treat Back Pain", "% of users who click on \"people also ask\" box",
  fun = ~ mean(.!=0, na.rm =TRUE),
  nudge_x = .005)

save_plot(plots[[item]], item, 10, 6.5)
```

## 1.15 Clicks to 2nd+ Google page

```{r}
item <- "Clicks to 2nd+ Google page"
table(full_data[[item]], useNA = "always")

plots[[item]] <- lollipop_chart(
  full_data, item, 
  "Very few Users Click on a Further Google Page", "% of users who click on a further google page",
  fun = ~ mean(.!=0, na.rm =TRUE),
  nudge_x = .0005, digits = .1)

save_plot(plots[[item]], item, 10, 6.5)
```


## Seconds to complete search task

```{r}
item <- "Seconds to complete search task"

# full_data %>%
#   group_by_at(item) %>%
#   summarize(n = n()) %>%
#   ggplot(aes(!!sym(item), n)) +
#   geom_point() +
#   geom_line() +
#   ggtitle("raw chart")

# quantile data with labels

plots[[item]] <- quantile_chart(
  full_data, item,
  "The Average Google Search Session Lasts 76 Seconds",
  "time (seconds)", "% of users who complete the task before time",
  meanlab = "Average : %s sec", qlab = "%s%% complete before %s sec",
  xmax = 250, nudge_x = 7
)

save_plot(plots[[item]], item, 9, 7)

## might need soem additional work
item_facets <- paste0(item,"_facets")
plots[[item_facets]] <- quantile_chart2(
  full_data, item,
  "Time to Complete Search By Query",
  "time (seconds)", "% of users who complete the task before time",
  meanlab = "Average: %s sec", qlab = "%s%% complete before %s sec",
  xmax = 250, nudge_x = 8)

save_plot(plots[[item_facets]], item_facets, 14, 16)

item2 <- paste0(item, "_2")
plots[[item2]] <- lollipop_chart(
  full_data, item, 
  "Depending on the Query the Search Takes an Average\nTime of 45 Sec to 90 Sec", "Time (seconds)",
  fun = ~ mean(., na.rm =TRUE),
  percent = FALSE,
  nudge_x = 5)

save_plot(plots[[item2]], item2, 10, 6.5)
```


## Total Clicks

```{r}
item <- "Total Clicks"
table(full_data[[item]], useNA = "always")

plots[[item]] <- quantile_chart(
  full_data, item,
  "Total Number of Clicks",
  "Time (seconds)", "% of users who clicked less than this amount",
  meanlab = "Average : %s times", qlab = "%s%% click %s times or less",
  xmax = 30, nudge_x = .8
)

save_plot(plots[[item]], item, 9, 7)

item_facets <- paste0(item,"_facets")
plots[[item_facets]] <- quantile_chart2(
  full_data, item,
  "Total Number of Clicks by Question",
  "Time (seconds)", "% of users who clicked less than this amount",
  meanlab = "Average: %s sec", qlab = "%s%% click %s times or less",
  xmax = 30, nudge_x = 1)

save_plot(plots[[item_facets]], item_facets, 14, 16)

item2 <- paste0(item, "_2")
plots[[item2]] <- lollipop_chart(
  full_data, item, 
  "Average Total Clicks", "Clicks",
  fun = ~ mean(., na.rm =TRUE),
  percent = FALSE,
  nudge_x = .4)

save_plot(plots[[item2]], item2, 9, 6.5)
```

## correlations

```{r}
data2 <-
  full_data %>%
  na.omit() %>%
  select(-c(1, 2, 3, 5, 9, 10, 11, 12, 13, 14, 15, 16, 17)) %>%
  select(-1) %>%
  select_if(is.numeric) %>%
  setNames(c("modified queries", "bounces", "pages visited", "seconds to complete", "total clicks"))

plots[["correlations"]] <- GGally::ggcorr(
  data2, nbreaks = 8, palette ='RdGy', label = TRUE, label_size = 5, label_color = 'white')
save_plot(plots[["correlations"]], "correlations", 11.5, 8.5)
```


```{r}
sum(full_data[["Seconds to complete search task"]]) /60/60
```




# 2. Save Results

For conveniencewe save our list of ggplot objects, though we'll directly
use the pictures in final.Rmd.

```{r}
saveRDS(plots, here::here("proc_data/plots.RDS"))
```

```{r convert-pdf-to-png, include = F}
pdfs <- list.files(here::here("plots"), pattern = "*.pdf")

setwd(here::here("plots", "png"))

for(pdf in pdfs) {
  pdf_convert(pdf = here::here("plots", pdf),
              format = "png", dpi = 300)
}
```


