---
title: "Google User Behaviour Study"
author: "FrontPage Data and Backlinko"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc_depth: 3
    toc_float: true
editor_options:
  chunk_output_type: console
---

<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.showtext = TRUE)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
plots <- readRDS(here::here("proc_data/plots.RDS"))
include_png <- function(item) {
  knitr::include_graphics(
    here::here("plots", "png", paste0(make.names(item), ".png")))
  } 
```

The total recording time was 2276 minutes (38 hours)


# 0. Introduction

The current lack of data from Google about the behavior of users has been the greatest frustration for SEOs. Although some previous studies have tried to analyze user behavior on Google, most of them are outdated as SERP features have changed over the past years.

This study intends to fill the gap and shed some timely and novel insights on how users interact with Google’s SERP features. 

In this study, we address the following research questions:

1. What percentage of users used the search suggestion?
2. What is the average time to first click?  
3. What percentage of users scroll to the bottom of the first page?
4. What percentage of users change their search query? 
5. What percentage of users bounces back to the search results and chooses a different result? (i.e.pogo-sticking)?
6. How many pages do users visit on average?
7. What percent of clicks go to organic search results?
8. What percent of clicks go to Google Adwords or paid listings? 
9. What percent of clicks go to video results?
10. What percent of clicks go to google maps listings?
11. What percent of clicks go to shopping results?
12. What percent of clicks go to "people also ask" box?
13. What percent of clicks go to page 2nd+ Google page? 
14. How long is the average Google search session? (after entering a search query and hitting enter)
15.	What´s the average number of clicks in a Google Search Session?
16. Do we see any relationship between key variables in a Google Search?


# 0.1 Methodology

**Step 1 Survey Design**:  We provided the survey respondents with a set of Google search queries. In order to provide a broad set of search queries, we settled for the following ones:   

1.	Commercial_1_pyhsical: find a car phone holder (assumption: Google shopping results)
2.	Commercial_2_service: find a credit card (assumptions: affiliate articles)
3.	Local: find a car accident lawyer (assumptions: ads)
4.	Informational_1: find how to cut your own hair (assumptions: videos)
5.	Informational_2: find how to treat back pain (assumptions: in-depth articles)
6.	Transactional: find supplements that may help with lower back pain
7.	Commercial_3_service: buy groceries online in your local area

You can find the survey questions here: [Link](https://docs.google.com/document/d/1HNIJ_mWbREtgWrVgm5EvbhTjxL8he_Ix-HnHVBuuKHQ/edit?usp=sharing)

**Step 2 Survey Tools and Screen Recording**: Secondly, we decided to screen record survey participants to derive useful data points for our study. Our survey tool of choice was surveygizmo.com, as it nicely integrated with the screen recording software addpipe.com. US-Participants for the study were recruited on Mechnical Turk. The survey instructions can be found [here](https://docs.google.com/document/d/1HNIJ_mWbREtgWrVgm5EvbhTjxL8he_Ix-HnHVBuuKHQ/edit#bookmark=id.w8e7mmaqaluj) and a sample screen recording video can be watched [here](https://us1-addpipe.s3-us-west-1.amazonaws.com/4f295537e6741ceea82cfdd0c5caebf9/xOpH5an8WIW30XkcyS6NsTqK5nBPhaeD.mp4). 

**Step 3 Data Annotation**: Thirdly, to consider only valid responses for the data annotation task, we reviewed each video individually to check whether instructions were followed properly. We then annotated the video data and entered each data point into a spread sheet. We collected data on 259 videos with a total length of 281 minutes.   

# 0.2 Overview of the respondents

Respondents provided information about their use of search engines.

We observe that Google is most commonly used by 94% of users.
Bing is the biggest competitor with a much smaller share of 2.7%.

76% of users use Google search multiple times a day, and 94% use it at least once
every day.

```{r}
include_png("engines_1")
include_png("engines2_1")
include_png("how_do_you_use_gs_1")
```

# 1. Use of suggested searches

We measure for each question what percentage of users used the search suggestion.
We find that users use them between 18% and 31% of the time, globally 23% of the time
on average.

```{r}
include_png("When typing the search query, did they select one of the suggested searches? (Y/N)_1")
```

# 2. Time to first click

Using the video timestamps we can assess the time when users click for the first
time. We find that the on average a user clicks first after 15 seconds and that
half of the users click between 5 seconds and 17 seconds after getting on the page.

The average time to first click, when we consider questions independently,
varies from 10 to 25 seconds.

```{r}
include_png("Seconds to first click (use check time stamping on video)_1")
include_png("Seconds to first click (use check time stamping on video)_facets_1")
include_png("Seconds to first click (use check time stamping on video)_2_1")
```

# 3. Scrolling to the bottom of the search page

On average 9% of users reach the bottom of the page, as we can expect 
this varies however significantly depending on the query, the most specific queries
leading to higher percentage. We find that to find a car phone holder,
as little as 3% of the users reach the bottom, while 17% (almost 6 times more)
reach it when searching for supplements to treat back pain.

```{r}
include_png("Did they scroll to the end of the Google Search Page (Y/N)?_1")
```

# 4. Modifications of the search query

In the majority of cases (85%), we find that users don't change their search
query at all. 11% change it once and only 4% change it 2 times or more. 

Modifying one's query or not depends a lot on the nature of the search.
Our data shows that the percentage of users who change their query can go from
under 5% to more than 35% when trying to find supplements for back pain.

```{r}
include_png("Times changed/modified search query_1")
include_png("Times changed/modified search query_2_1")
```

# 5. Pogo sticking

We measure how many times searchers clicks a result, then bounces back to the 
search results page and chooses a different result. We find that overall the
bounce rate is small, 83% never bounce while only 5% bounce more than once. 

Depending on the question, this percentage of users who bounce at least once
varies in the of 10% to 30%.

```{r}
include_png("Times searcher clicks a result, then bounces back to the search results page and chooses a different result_1")
include_png("Times searcher clicks a result, then bounces back to the search results page and chooses a different result_2_1")
```

# 6. Number of pages visited

We find that most users visit only one page, but for some specific queries the
average can go above 2.

```{r}
include_png("Number of pages visited_1")
include_png("Number of pages visited_2_1")
```

# 7. Clicks on organic search results

We find that most users click on organic search results at least once.
However two questions stand out, few users click on organic search results when
looking for a car accident lawyer or how to cut one's hair.

```{r}
include_png("Clicks on organic search results_1")
include_png("Clicks on organic search results_2_1")
```

# 8. Clicks on Google AdWords or paid listings

We find that users click on Google Adwords links or paid listings 19% of the
time overall but depending on the query this can go from 0% to 30%.

```{r}
include_png("Clicks on Google AdWords/paid listings_1")
include_png("Clicks on Google AdWords/paid listings_2_1")
```

# 9. Clicks on video results

We measure how often users click on video links. Our results are very polarized
here because for a single question around 95% of users clicked on a video result
while in all other cases virtually no one did.

```{r}
include_png("Clicks on video results_2_1")
```


# 10. Clicks on Google Maps or local listings

We find that users click on Google Maps or local listings 40% of the time
when the query is about finding a car accident lawyer, and very few times
otherwise.

Additionally, our data indicates that when the user clicked on Google Maps or local 
listings, their chance of clicking on one of the 3 first listings is 97%.

```{r}
include_png("Clicks on Google Maps/local listings_1")
include_png("Clicks on Google Maps/local listings_2_1")
```

# 11. Clicks on Google Shopping results

Almost 20% of users click on Google Shopping results when the question is about
finding a car phone holder, and 5% of them click them when looking for back
pain supplements. In other cases virtually no one clicks on  Google Shopping results.

```{r}
include_png("Clicks on Google Shopping results_1")
```

# 12. Clicks "people also ask" box

Almost 15% of users click the "people also ask" box when the question is about
finding supplements forback pain. For other queries this varies from 0% to 3%.

```{r}
include_png("Clicks \"people also ask\" box_1")
```

# 13. Clicks to 2nd+ Google page

We find that very few users (0.5%) click on the second google search page or further.
Looking at the distinct questions, we see that users looking for supplemenetation
to treat back pain are the most likely to reach the second page or further (1.5%).

```{r}
include_png("Clicks to 2nd+ Google page_1")
```

# 14. Time taken to complete the search

The average search is computed in 76 seconds, and we find that
half of the searches are completed in 30 seconds to 90 seconds.

```{r}
include_png("Seconds to complete search task_1")
include_png("Seconds to complete search task_facets_1")
include_png("Seconds to complete search task_2_1")
```

# 15. Total Clicks

During an average search a user clicks 7 times on average, 
in our dataset is computed in 76 seconds, and we find that
half of the searches are completed in 30 seconds to 90 seconds.

```{r}
include_png("Total Clicks_1")
include_png("Total Clicks_facets_1")
include_png("Total Clicks_2_1")
```

# 16. Relationships between variables

We observe some important correlations between some variables of our study.
In particular the number of modified queries, the number of bounces, and
the number of seconds to complete a search show correlations from 0.7 to 0.9.

This may indicate that users faced with a challenging Google search try different strategies.

```{r}
include_png("correlations_1")
```


