---
title: "Google User Study"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc_depth: 3
    toc_float: true
editor_options:
  chunk_output_type: console
---

<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.showtext = TRUE)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
plots <- readRDS(here::here("proc_data/plots.RDS"))
include_png <- function(item) {
  knitr::include_graphics(
    here::here("plots", paste0(make.names(item), ".png")))
  } 
```


# 0. Introduction


# Use of suggested searches

We measure for each question what percentage of users used the search suggestion.
We find that users use them between 18% and 23% of the time, globally 23% of the time
on average.

```{r}
item <- "When typing the search query, did they select one of the suggested searches? (Y/N)"
include_png(item)
```

# Time to first click (use check time stamping on video)

Using the video timestamps we can assess the time when users click for the first
time. We find that the on average a user clicks first after 15 seconds and that
half of the users click between 5 seconds and 17 seconds after getting on the page.

The average time to first click, when we consider questions independently,
varies from 10 to 25 seconds.

```{r}
include_png("Seconds to first click (use check time stamping on video)")
include_png("Seconds to first click (use check time stamping on video)_2")
```

# Scrolling to the bottom of the search page

On average 9% of users reach the bottom of the page, as we can expect 
this varies however significantly depending on the query, the most specific queries
leading to higher percentage. We find that to find a car phone holder,
as little as 3% of the users reach the bottom, while 17% (almost 6 times more)
reach it when searching for supplements to treat back pain.

```{r}
include_png("Did they scroll to the end of the Google Search Page (Y/N)?")
```

# Modifications of the search query

In the big majority of cases (85%), we find that users don't change their search
query at all. 11% change it once and only 4% change it 2 or more. 

Modifying one's query or not depends a lot on the nature of the search.
Our data shows that the percentage of users who change their query can go from
under 5% to more than 30% depending on the nature of the search.

```{r}
include_png("Times changed/modified search query")
include_png("Times changed/modified search query_2")
```

# Bounce

We measure how many times searcher clicks a result, then bounces back to the 
search results page and chooses a different result. We find that overall the
bounce rate is small, 83% never bounce while only 5% bounce more than once. 

Depending on the question, this percentage of users who bounce at least once
varies in the of 10% to 30%.

```{r}
include_png("Times searcher clicks a result, then bounces back to the search results page and chooses a different result")
include_png("Times searcher clicks a result, then bounces back to the search results page and chooses a different result_2")
```

# Number of pages visited

We find that most users visit only one page, but for some specific queries the
average can go above 2.

```{r}
include_png("Number of pages visited")
include_png("Number of pages visited_2")
```

# Clicks on organic search results

We find that most users click on organic search results at least once.
However two questions stand out, few users click on organic search results when
looking for a car accident lawyer or how to cut one's hair.

```{r}
include_png("Clicks on organic search results")
include_png("Clicks on organic search results_2")
```

# Clicks on Google AdWords or paid listings

We find that users click on Google Adwords links or paid listings 19% of the
time overall but depending on the query this can go from 0% to 30%.

```{r}
include_png("Clicks on Google AdWords/paid listings")
include_png("Clicks on Google AdWords/paid listings_2")
```

# Clicks on video results

We measure how often users click on video links. Our results are very polarizing
here because for a single question around 95% of users clicked on a video result
while in all other cases virtually no one did.

```{r}
include_png("Clicks on video results_2")
```


# Clicks on Google Maps or local listings

We find that users click on Google Maps or local listings 40% of the time
when the query is about finding a car accident lawyer, and very few times
otherwise.

Additionally, our data indicates that when the user clicked on Google Maps or local 
listings, their chance of clicking on one of the 3 first listings is 97%.

```{r}
include_png("Clicks on Google Maps/local listings")
include_png("Clicks on Google Maps/local listings_2")
```

# Clicks on Google Shopping results

Almost 20% of users click on Google Shopping results when the question is about
finding a car phone holder, and 5% of them click them when looking for back
pain supplements. In other cases virtually no one clicks on  Google Shopping results.

```{r}
include_png("Clicks on Google Shopping results")
```

# Clicks "people also ask" box

Almost 15% of users click the "people also ask" box when the question is about
finding supplements forback pain. For other queries this varies from 0% to 3%.

```{r}
include_png("Clicks \"people also ask\" box")
```

# Clicks to 2nd+ Google page

We find that very few users (0.5%) click on the second google search page or further.
Looking at the distinct questions, we see that users looking for supplemenetation
to treat back pain are the most likely to reach the second page or further (1.5%).

```{r}
include_png("Clicks to 2nd+ Google page")
```

# Seconds to complete search task

```{r}
include_png("Seconds to complete search task")
include_png("Seconds to complete search task_2")
```

# Total Clicks

```{r}
include_png("Total Clicks")
include_png("Total Clicks_2")
```



