---
title: "Google User Study"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc_depth: 3
    toc_float: true
editor_options:
  chunk_output_type: console
---

<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.showtext = TRUE)
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})
plots <- readRDS(here::here("proc_data/plots.RDS"))
```


# 0. Introduction


# When typing the search query, did they select one of the suggested searches? (Y/N)


```{r}
plots[["When typing the search query, did they select one of the suggested searches? (Y/N)"]]
```

# Seconds to first click (use check time stamping on video)

```{r}
plots[["Seconds to first click (use check time stamping on video)"]]
```


# Did they scroll to the end of the Google Search Page (Y/N)?

```{r}
plots[["Did they scroll to the end of the Google Search Page (Y/N)?"]]
```


# Times changed/modified search query

```{r}
plots[["Times changed/modified search query"]]
```

# Times searcher clicks a result, then bounces back to the search results page and chooses a different result

```{r}
plots[["Times searcher clicks a result, then bounces back to the search results page and chooses a different result"]]
```


# Number of pages visited

```{r}
plots[["Number of pages visited"]]
```


# Clicks on organic search results

```{r}
plots[["Clicks on organic search results"]]
```


# Clicks on Google AdWords/paid listings

```{r}
plots[["Clicks on Google AdWords/paid listings"]]
```


# Clicks on video results

```{r}
plots[["Clicks on video results"]]
```


# Clicks on Google Maps/local listings

```{r}
plots[["Clicks on Google Maps/local listings"]]
```


# If clicked on Google Maps/local listing, did they click on one of the first three listings?

Yes, 97% of the time


# Clicks on Image blocks

```{r}
plots[["Clicks on Image blocks"]]
```


# Clicks on Google Shopping results

```{r}
plots[["Clicks on Google Shopping results"]]
```


# Clicks "people also ask" box

```{r}
plots[["Clicks \"people also ask\" box"]]
```

# Clicks to 2nd+ Google page

```{r}
plots[["Clicks to 2nd+ Google page"]]
```

# Seconds to complete search task

```{r}
plots[["Seconds to complete search task"]]
```

# Total Clicks

```{r}
plots[["Total Clicks"]]
```



