---
title: "Questions"
author: "Antoine Fabri"
date: "17 août 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions from google doc

```{r, echo = FALSE}
full_data <- readRDS(here::here("proc_data/clean_data.RDS"))
```

Questions from the google doc are answered here with counts and some comments.

I can't completely elucidate why we can have many clicks on organic searches without bounce, but the data definitely says so.

I give some hypothesis as to why.


## Ignored questions

The following questions were ignored as decided on whatsapp

> “Almost 20% of users click on Google Shopping results”. What is the exact percentage?

> Actually: please provide exact percentages for all data points. Ie. “We find that users click on Google Maps or local listings 40% of the time”.

> “Almost 15% of users click the “people also ask” box when”. What is the exact percentage?

> We find that the on average a user clicks first after 15 seconds. What is the exact average number?

> On average 9% of users reach the bottom of the page. What is the exact number?


## 7. bounce vs clicks

> 83% never bounce vs. During an average search a user clicks 7 times on average.
> How can both of these things be true? Is it that those that DO bounce end up clicking on lots of things?*

Those who do bounce click more (12.4 times on average), but those who don't
bounce dont click much less than 7 times (5.8 on average).

```{r}
mean(full_data$"Total Clicks"[
  full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0
], na.rm = TRUE)

mean(full_data$"Total Clicks"[
  full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" != 0
], na.rm = TRUE)

table(
  clicks = full_data$"Total Clicks", 
  bounces = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result")

table(
  clicks = full_data$"Total Clicks", 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)
```

We can try to see on hat they do click

```{r}
table(
  clicks = full_data$"Clicks on organic search results", 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)


table(
  clicks = full_data$"Clicks on Google AdWords/paid listings", 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)


table(
  clicks = full_data$"Clicks on video results", 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)


table(
  clicks = full_data$"Clicks on Google Maps/local listings", 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)


table(
  clicks = full_data$"Clicks on Image blocks", 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)


table(
  clicks = full_data$"Clicks on Google Shopping results", 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)

table(
  clicks = full_data$"Clicks \"people also ask\" box" , 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)

table(
  clicks = full_data$"Clicks to 2nd+ Google page" , 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)
```



## 8. page visits vs clicks

> The majority (59%) of Google users visit a single page vs a user clicks 7 times on average.
> How can both of these things be true?

People who visit a single page click 5 times on average, the rest clicks 9.5 times
on average.

See above to see on what they click, visited pages include only non google pages.

```{r}

mean(full_data$"Total Clicks"[
  full_data$"Number of pages visited" == 1
], na.rm = TRUE)

mean(full_data$"Total Clicks"[
  full_data$"Number of pages visited" != 1
], na.rm = TRUE)

table(
  clicks = full_data$"Total Clicks", 
  pages_visited = full_data$"Number of pages visited")

table(
  clicks = full_data$"Total Clicks", 
  one_page_visited = full_data$"Number of pages visited" == 1)
```

## 9. bounce vs page visits

> 83% never bounce vs. 59% of Google Users Click on a Single Result During Their Search Session.
> How can both things be true? 

I suppose that the definition of a page to bounce from is more generous than the definition of a page visited.

We have the following definition : 


*Number of pages visited/viewed* : 

> Number of different pages a searcher visited (exlcuding google pages and surveygizmo).
> A pageview can be the initial load of a page, a reload or a revisit to the page. If the searcher only stayed always on a goolge property, please enter the value 0.

The key might be in "exlcuding google pages and surveygizmo" here, the bounces
from these pages might be counted while the page visits are not.

We saw in 7. however that some users clicked on 5 organic links with no bounce counted.

The video might be interpreted as if a bounce occurs only
when we open a new tab, and not if we use the "back" button from the browser.

Another possibility is that a bounce is counted as such only if user goes back 
immediately, and not if they stayed a few seconds to read the content in detail.


```{r}
table(
  pages_visited = full_data$"Number of pages visited", 
  bounces = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result")


table(
  visits_one_page = full_data$"Number of pages visited" == 1, 
  no_bounce = full_data$"Times searcher clicks a result, then bounces back to the search results page and chooses a different result" == 0)
```


## 10. Clicks on organic results

> https://www.screencast.com/t/3418UxUuba. 65%. Shouldn’t this be 76% (49+10+17)? Based on: https://www.screencast.com/t/PQ1aMo8JD 

The linked chart doesn't show the 17 figure, it shows 7, so the sum would be 66%, given the figures are rounded it's consistent with the 65 figure.

